---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(binomial)
```


## Binomial
The package "binomial" simulates the process of getting the probability of a specific number of successes given the number of trials, the number of successes, and the probability to get that success.


## Caculating probability
Log in the data you have in function bin_probability in order: successes, trials, and probability.
```{r}
bin_probability(2,5,0.5)
```


## Showing table
The "bin_distribution" function gives you a table of probabilities corresponding to each success (from 0 to trials). Enter trials and probability. The table has two classes: "bindis" and "data.frame":
```{r}
bin_distribution(5,0.5)
```
The "bin_cumulative" function gives you a table of cumulative probabilities corresponding to the successes. Enter trials and probability. The table has two classes: "bincum" and "data.frame"
```{r}
bin_cumulative(5,0.5)
```


## Summary
Function "bin_variable" returns a list with class "binvar" and method "print.binvar" gives a short summary of object with class "binvar" 
```{r}
bin1 <- bin_variable(10,0.3)
bin1
```
Function "summary.binvar" returns a list with full elements and class "binvar" and method "print.summary.binvar" gives a full summary of object with class "binvar" 
```{r}
bin1 <- bin_variable(10,0.3)
binsum1 <- summary(bin1)
binsum1
```


## Plot of relative frequencies
You can use function "plot()" to create a graphic with the relative frequencies of a series of trials. Input must be a data frame with two classes: "bindis" and "data.frame" to create a **histogram**
```{r,fig.show="hold"}
dis1 <- bin_distribution(5,0.5)
plot(dis1)
```
You can use function "plot()" to create a graphic with the cumulative frequencies of a series of trials. Input must be a data frame with two classes: "bincum" and "data.frame" to create a **line graph**
```{r,fig.show="hold"}
dis2 <- bin_cumulative(5,0.5)
plot(dis2)
```





